---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# saeHB.twofold

<!-- badges: start -->
<!-- badges: end -->

Provides several functions for area and subarea level of small area estimation under Twofold Subarea Level Model using hierarchical Bayesian (HB) method with Univariate Normal distribution for variables of interest. Some dataset simulated by a data generation are also provided. The 'rjags' package is employed to obtain parameter estimates using Gibbs Sampling algorithm. Model-based estimators involves the HB estimators which include the mean, the variation of mean, and the quantile. For the reference, see Rao and Molina (2015), Torabi (2014), and Leyla Mohadjer et.al(2007)

## Author
Reyhan Saadi, Azka Ubaidillah

## Maintaner
Reyhan Saadi <221810557@stis.ac.id> or <aansum99@gmail.com>

## Function
* `NormalTF()` This function gives estimation of subarea and area means simultaneously under Twofold Subarea Small Area Estimation Model Using Hierarchical Bayesian Method with Normal distribution based on model in Torabi (2014)

## Installation
You can install the development version of saeHB.twofold from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("reymath99/saeHB.twofold")
```

## Example

This is a basic example of using NormalTF function to make an estimate based on sample data in this package

```{r example}
library(saeHB.twofold)
data(dataTwofold)
#for dataset with nonsampled subarea use dataTwofoldNS
#fitting model
model=NormalTF(y~x1+x2,vardir="vardir",area = "codearea",weight = "w",data=dataTwofold)
```

Extract subarea mean estimation
```r
model$Est_sub
```

Extract area mean estimation
```r
model$Est_area
```

Extract coefficient estimation $\beta$
```r
model$coefficient
```

Extract estimation of subarea random effect variance $\sigma^2_u$ and area random
effect variance $\sigma^2_v$
```{r}
model$refvar
```

Calculate relative standard error or CV
```r
CV=(model$Est_sub$SD)/(model$Est_sub$Mean)*100
#cv summaries
summary(CV)
```


## References
* Mohadjer, L.K., Rao, J.N., Liu, B., Krenzke, T., & Kerckhove, W.V. (2007). Hierarchical Bayes Small Area Estimates of Adult Literacy Using Unmatched Sampling and Linking Models.
* Torabi, M., & Rao, J.N. (2014). On small area estimation under a sub-area level model. J. Multivar. Anal., 127, 36-55.
* Rao, J.N.K & Molina. (2015). Small Area Estimation 2nd Edition. New York: John Wiley and Sons, Inc.
